\Large Analyzing the Supreme Court Citation Network

### 2018-01-02 Tex/paper.tex
added short conclusion

MAJOR LIMITATION---DO NOT CONSIDER SIGN OF CASES

>>>>

We present a methodology for studying citations between US Supreme Court opinions at the dyadic level, as a network. This methodology---the citation-TERGM---enables researchers to include both exogenous covariates such as the ideological predisposition and age of a case, and dependence terms, such as transitivity and reciprocity, as explanations for citation formation. We apply this methodology to a network that includes all Supreme Court cases decided between 1937 and 2001. We find, somewhat counterintuitively, that Supreme Court citations are highly reciprocal. We also find that citations are driven by dependencies such as triad closure, popularity, and activity. The dependence effects that we identify are as substantively and statistically significant as the effects of the exogenous covariates we include in the model. The summary result from this analysis is that theoretical models of Supreme Court citation formation should consider both the effects of case characteristics and the structure of past citations.

We recognize several limitations of the current analysis, which should be addressed in future iterations of this work or in future studies. First, our theoretical claims and analyses treat all citations---positive and negative---as equivalent. Both data and methodological limitations will need to be overcome to consider these two citation types. Second, there is nothing in the c-TERGM that governs the generation of new cases (i.e., cases are assumed to arise exogenously, unrelated to the history of the citation network). As new cases are often taken up by the Supreme Court in order to test, clarify, and/or challenge existing precedents, it is likely inappropriate to assume that new cases arise exogenous to the existing citation network. Overcoming this limitation would require methodological innovation in the c-TERGM as well as theoretical development regarding exactly how citation structure might predict case emergence. Third, the data used in this study does not cover the most recent history of the Court. Our data ends in 2001---missing the tenure of the most recent chief justice, and more than fifteen terms. To overcome this limitation we would need to extend the citation data beyond that collected by Fowler and colleagues.
